Asymmetric relationships and their effects on coexistence

### 2023-09-18 paper/RefereeResponses2.tex

\noindent ***\emph{Thank you for the very positive feedback and previous comments which helped to improve our manuscript!} \\

\noindent \textbf{Comments of referee 3:} \\

\noindent C5) I thank the authors for the change and the nice discussion/replies to my questions. I especially like the new figure 2 which greatly helped my understanding of how to remove ATA. \\

\noindent ***\emph{Many thanks for the positive feedback which improved our manuscript to become more understandable to other readers as well!} \\

@@

Page 2, Lines 59-60 “coexistence into the contributions of various mechanisms, with names such as storage effects (Chesson1994). Storage effects refer to….. Storage effects are reviewed conceptually below and defined formally in Theory. \\

\noindent ***\emph{We did as requested.} \\

\noindent C10)  Page 2, Line 60: Start a new paragraph with the sentence “MCT has been applied to several systems…” \\

\noindent ***\emph{This seemed, to us, to be an odd request, as the sentence which followed this one is the 
last in the paragraph, so putting a new paragraph break where the referee suggested would make a very short, two
sentence paragraph, with no clear topic sentence. Furthermore, the purpose of the paragraph this sentence
is a part of is to introduce MCT, a purpose which is definitely served by these two sentences. So, to us,
these sentences seemed to fit better where they were than in a new paragraph on their own. 
So we thought about why the referee may have made such
request and whether we might be able to address the underlying issue. It seemed to us the confusion might have come
from the fact that, whereas the paragraph starts with general MCT, it then transitions to storage effects, and 
then transitions back
to general MCT at the point of the two sentences the referee has asked us to separate. 
Whereas storage effects are part of MCT, so it makes sense to mention them in a paragraph about MCT,
the transition to storage effects and then back to general MCT might have been confusing. So we moved the
two sentences in question to earlier in the paragraph. We think this is an improvement and should, hopefully,
address the underlying issue as well as streamlining the transition to the following paragraph.}

### 2023-09-25 paper/Paper.Rnw
changes to the readme and Reuman affiliations
fixed small ttypo

\author[a,b]{Pimsupa Jasmin Albert}
\author[a,c,*]{Daniel C. Reuman}

\affil[a]{Department of Ecology and Evolutionary Biology and Center for Ecological Research, University of Kansas}
\affil[b]{Environmental Studies Program and Department of Biology, University of Oregon}
\affil[c]{Laboratory of Populations, Rockefeller University}
\affil[*]{Corresponding author, reuman@ku.edu}

@@

%more stuff that applies to both
For both versions of the lottery model, 
fecundities directly reflected 
the environment, i.e., the $E_i$ of Theory was set equal to $B_i$. 
Competition, $C_i(t)$, in the lottery model occurs at the stage of juveniles occupying open sites:
$C_i$ was taken to be the number of new offspring
divided by the number of open sites, $C_i(t)=( B_1(t)N_1(t)+B_2(t)N_2(t) )/(\delta N$), which
does not depend on $i$. These choices for fulfill the assumption of Theory 
that $r_i(t)$ is an increasing function of $E_i(t)$ and a decreasing function of $C_i(t)$ 
(SI section \ref{SI-SIsect:TheoryForLottery}).

>>>>

\author[a,b]{Pimsupa Jasmin Albert}
\author[a,*]{Daniel C. Reuman}

\affil[a]{Department of Ecology and Evolutionary Biology and Center for Ecological Research, University of Kansas}
\affil[b]{Environmental Studies Program and Department of Biology, University of Oregon}
\affil[*]{Corresponding author, reuman@ku.edu}

@@

%more stuff that applies to both
For both versions of the lottery model, 
fecundities directly reflected 
the environment, i.e., the $E_i$ of Theory was set equal to $B_i$. 
Competition, $C_i(t)$, in the lottery model occurs at the stage of juveniles occupying open sites:
$C_i$ was taken to be the number of new offspring
divided by the number of open sites, $C_i(t)=( B_1(t)N_1(t)+B_2(t)N_2(t) )/(\delta N$), which
does not depend on $i$. These choices fulfill the assumption of Theory 
that $r_i(t)$ is an increasing function of $E_i(t)$ and a decreasing function of $C_i(t)$ 
(SI section \ref{SI-SIsect:TheoryForLottery}).
